---
title: "Set-up"
output:
  html_document:
    toc: true
    include:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get an account on GitHub

If you don't already have an account on GitHub, go to [github.com](github.com) and click the "sign up" link near upper right 
of the page.  It is pretty self-explanatory.  Go ahead and get a **free** account.  

The free GitHub account does not have private repositories.  Everything is public and viewable.  You can upgrade (for money) and get private repositories.  Or _if you are a student_, you can get private repositories from GitHub for free.  Go to [https://education.github.com/pack](https://education.github.com/pack) to sign up for your free student pack.  You will need to upload proof that you are a student or faculty.

## Install GitHub Desktop

1. Go to [desktop.github.com](https://desktop.github.com/) and install.
2. Open GitHub Desktop, go to 'GitHub Desktop > Preferences' menu.  
3. Under 'Accounts', sign into your GitHub account.
3. Under 'Git', enter your name (or initials) and the email you used for your GitHub account.

## Install RStudio and R

1. **RStudio:** Install the latest "development" version of RStudio becuase it has features that we may want to use during this course.  Get it from [https://www.rstudio.com/products/rstudio/download/preview/](https://www.rstudio.com/products/rstudio/download/preview/) and install the appropriate one for your OS.

1. **R:**  Make sure you have the latest version of R.  
Go to [https://cran.r-project.org/](https://cran.r-project.org/) and find the download link for your computer system.

1. **bookdown:** package.  This automatically installs many packages that are useful for authoring reproducible research.  We want the latest development version, which 
can be obtained from GitHub by issuing the following commans at the R prompt (i.e. in the console window of RStudio:)
```{r get-bd, eval=FALSE}
install.packages("devtools")  
devtools::install_github("rstudio/bookdown")
```

1. Install **other packages** that we are going to be need. 
```{r get-packages, eval=FALSE}
install.packages("knitr")  
install.packages("rmarkdown")  
install.packages("ggplot2")  
install.packages("stringr")  
```

## Create a workshop folder

Create a folder/directory on your computer for the workshop materials.  You can create it anywhere you want.  But name it `RWorkflow` just so we all use the same folder name for the workshop.

## Disqus forum

I have added a Disqus forum to the website.  [Create an account](https://disqus.com/) if you would like to be able to add comments/questions.  This will allow people to pose questions to the group and allow me (and others) to answer.
